TODO \thanks{ The original version of this paper is entitled ``Interactive Checks for Coordination Avoidance'' and was published in PVLDB Vol.\ 12. }

### 2020-05-16 doc/sigmod_paper/sections/conclusion.tex
First round of cuts.
The paper is now 8 pages without citations. We need 8 pages with
citations, so we need to trim another page or so. I'll probably shrink
the evaluation a bit more, shrink the related works a bit more, shrink
segmented invariant confluence a bit more and see what we end up with.

\section{Conclusion}
This paper revolved around two major contributions.
%
First, we developed a deeper understanding of \invariantclosure{} and
\invariantconfluence{} by looking at the two criteria with reachability in
mind. We found that \invariantclosure{} fails to incorporate a notion of
reachability, and using this intuition, we developed conditions under which
\invariantclosure{} and \invariantconfluence{} are equivalent. We implemented
this insight in an interactive \invariantconfluence{} decision procedure
that automatically checks whether an object is \invariantconfluent{}, with the
assistance of a programmer.

Second, we proposed a new consistency model and generalization of
\invariantconfluence{}, segmented \invariantconfluence{}, that can be used to
replicate non-\invariantconfluent{} objects with a small amount of coordination
while still preserving their invariants. We found that segmented
\invariantconfluence{} naturally subsumes existing techniques for maintaining
invariants of replicated objects (e.g.\ locking and escrow transactions), and
we developed an interactive decision procedure for segmented
\invariantconfluence{}.

Through our evaluation, we found that our decision procedures could analyze a
number of realistic workloads, each in less than a second. We also showed that
segmented \invariantconfluence{} can significantly outperform linearizable
replication for low-coordination workloads.

>>>>

\section{Conclusion}
This paper revolved around two major contributions.
%
First,
% we developed a deeper understanding of \invariantclosure{} and
% \invariantconfluence{} by looking at the two criteria with reachability in
% mind.
we found that \invariantclosure{} fails to incorporate a notion of
reachability, and using this intuition, we developed conditions under which
\invariantclosure{} and \invariantconfluence{} are equivalent. We implemented
this insight in an interactive \invariantconfluence{} decision procedure
that automatically checks whether an object is \invariantconfluent{}, with the
assistance of a programmer.
%
Second, we proposed a new consistency model and generalization of
\invariantconfluence{}, segmented \invariantconfluence{}, that can be used to
replicate non-\invariantconfluent{} objects with a small amount of coordination
while still preserving their invariants.
% We found that segmented
% \invariantconfluence{} naturally subsumes existing techniques for maintaining
% invariants of replicated objects (e.g.\ locking and escrow transactions), and
% we developed an interactive decision procedure for segmented
% \invariantconfluence{}.

% Through our evaluation, we found that our decision procedures could analyze a
% number of realistic workloads, each in less than a second. We also showed that
% segmented \invariantconfluence{} can significantly outperform linearizable
% replication for low-coordination workloads.

### 2020-05-16 doc/sigmod_paper/sections/interactive_decision_procedure.tex
First round of cuts.
The paper is now 8 pages without citations. We need 8 pages with
citations, so we need to trim another page or so. I'll probably shrink
the evaluation a bit more, shrink the related works a bit more, shrink
segmented invariant confluence a bit more and see what we end up with.

\subsection{The Decision Procedure}
A user provides \algoref{InteractiveDecisionProcedure} with an object $O = (S,
\join)$, a start state $s_0$, a set of transactions $T$, and an invariant
$I$. The user then interacts with \algoref{InteractiveDecisionProcedure} to
iteratively eliminate unreachable states from the invariant. Meanwhile, the
algorithm leverages an \invariantclosure{} decision procedure to either (a)
conclude that $O$ is or is not \sTIconfluent{} or (b) provide counterexamples
to the user to help them eliminate unreachable states. After all unreachable
states have been eliminated from the invariant,
\thmref{IclosureEquivalentIconfluence} allows us to reduce the problem of
\invariantconfluence{} directly to the problem of \invariantclosure{}, and the
algorithm terminates.
%
We now describe \algoref{InteractiveDecisionProcedure} in detail. An example of
how to use \algoref{InteractiveDecisionProcedure} on \exampleref{Z2} is given
in \figref{DecisionProcedureExample}.

@@

\subsection{Limitations}
Our interactive \invariantconfluence{} decision procedure has two
limitations. First, \algoref{InteractiveDecisionProcedure} requires an
\invariantclosure{} decision procedure, but determining \invariantclosure{} is
undecidable in general.
%
\begin{techreport}

  For example, let $O_p = (S, \join)$ where $S$ is the set of all programs and
  $s_1 \join s_2 = p$ for some fixed program $p$. Letting $I$ be the set of all
  programs that terminate, determining if $O_p$ is \Iclosed{} is tantamount to
  determining if $p$ terminates.
\end{techreport}
%
In practice, we can implement an \invariantclosure{} decision procedure using
an SMT solver like Z3 that works well on simple objects, invariants, and merge
operators (e.g., integers, tuples, infinite sets, bit vectors, linear
constraints, basic arithmetic, tuple projection, basic set operations, bit
arithmetic). But, SMT solvers are mostly unable to analyze more complex
constructs (e.g., finite lists~\cite{kroning2009proposal}, graphs, recursive
algebraic data types, nonlinear constraints, merge operators that contain loops
or recursion).

Second, \algoref{InteractiveDecisionProcedure} relies on a user to identify
unreachable states. As we saw in \figref{DecisionProcedureExample}, the set of
unreachable states can sometimes be clear, especially if there's a noticeable
pattern in the set of reachable states. However, if the set of transactions is
large or complex or if the merge operator is complex, then reasoning about
unreachable states can be difficult.  Unlike with reachable states---where
verifying that a state is reachable only requires thinking of a single way to
reach the state---verifying that a state is unreachable requires a programmer
to reason about a large number of system executions and conclude that
\emph{none} of them can lead to the state. In the future, we plan on exploring
ways to help a user reason about unreachable states and ways to discover sets of
unreachable states automatically.

\begin{techreport}
  \subsection{Tolerating User Error}
  \algoref{InteractiveDecisionProcedure} is an \emph{interactive} decision
  procedure. It requires that a user classify states as reachable or
  unreachable.  To err is human, so what happens when a user incorrectly
  classifies a state?  There are two possible errors that can be made, and
  \algoref{InteractiveDecisionProcedure} can be made robust to both.

  \textbf{A user can label an unreachable state as reachable.}
  In this case, \Helper{} might erroneously find $s_1$ and $s_2 \in R$ and
  return false, concluding that $O$ is not \sTIconfluent{} even when it is.
  This is inconvenient, but not catastrophic. We can modify
  \algoref{InteractiveDecisionProcedure} so that \Helper{} requires that
  whenever a user labels a state $s$ as \sTIreachable{}, they must also provide
  an \sTIreachable{} expression $e$ that evaluates to $s$. Here, $e$ acts a
  proof that certifies that $s$ is indeed reachable. This increases the burden
  on the user but completely eliminates this type of user error.

  \textbf{A user can label a reachable state as unreachable.}
  In this case, \IsIclosed$(O, I - NR)$ might return true, even though $O$ is
  not \sTIconfluent. Thus, a user might falsely believe their distributed
  object to be \sTIconfluent{} even though it isn't, and eventually one replica
  of their distributed object might enter a state that violates the invariant.
  %
  We can mitigate this in two ways. First, we can aggressively expand $R$
  automatically. If a user ever labels a state $s$ as unreachable, but $s \in
  R$, we can notify the user of their mistake. Second, \Helper{} returns true
  when $O$ is \iclosed{(I - NR)} for some $NR$, so $O$ \emph{is}
  \sticonfluent{s_0}{T}{I-NR} (even though it might not be \sTIconfluent{}).
  Thus, when a user replicates their distributed object across a set of
  servers, they can deploy with the invariant $I - NR$ instead of $I$. If $NR$
  is correct and only contains unreachable states, then deploying with $I - NR$
  is equivalent to deploying with $I$. If $NR$ is incorrect and contains some
  \sTIreachable{} states, then some of these states are artificially made
  unreachable, but the system is still guaranteed to never produce a state
  that violates $I$.
\end{techreport}

>>>>

% \subsection{The Decision Procedure}
A user provides \algoref{InteractiveDecisionProcedure} with an object $O = (S,
\join)$, a start state $s_0$, a set of transactions $T$, and an invariant
$I$. The user then interacts with \algoref{InteractiveDecisionProcedure} to
iteratively eliminate unreachable states from the invariant. Meanwhile, the
algorithm leverages an \invariantclosure{} decision procedure to either (a)
conclude that $O$ is or is not \sTIconfluent{} or (b) provide counterexamples
to the user to help them eliminate unreachable states. After all unreachable
states have been eliminated from the invariant,
\thmref{IclosureEquivalentIconfluence} allows us to reduce the problem of
\invariantconfluence{} directly to the problem of \invariantclosure{}, and the
algorithm terminates.
%
We now describe \algoref{InteractiveDecisionProcedure} in detail. An example of
how to use \algoref{InteractiveDecisionProcedure} on \exampleref{Z2} is given
in \figref{DecisionProcedureExample}.

@@

% \subsection{Limitations}
% Our interactive \invariantconfluence{} decision procedure has two
% limitations. First, \algoref{InteractiveDecisionProcedure} requires an
% \invariantclosure{} decision procedure, but determining \invariantclosure{} is
% undecidable in general.
% %
% In practice, we can implement an \invariantclosure{} decision procedure using
% an SMT solver like Z3 that works well on simple objects, invariants, and merge
% operators (e.g., integers, tuples, infinite sets, bit vectors, linear
% constraints, basic arithmetic, tuple projection, basic set operations, bit
% arithmetic). But, SMT solvers are mostly unable to analyze more complex
% constructs (e.g., finite lists~\cite{kroning2009proposal}, graphs, recursive
% algebraic data types, nonlinear constraints, merge operators that contain loops
% or recursion).
%
% Second, \algoref{InteractiveDecisionProcedure} relies on a user to identify
% unreachable states. As we saw in \figref{DecisionProcedureExample}, the set of
% unreachable states can sometimes be clear, especially if there's a noticeable
% pattern in the set of reachable states. However, if the set of transactions is
% large or complex or if the merge operator is complex, then reasoning about
% unreachable states can be difficult.  Unlike with reachable states---where
% verifying that a state is reachable only requires thinking of a single way to
% reach the state---verifying that a state is unreachable requires a programmer
% to reason about a large number of system executions and conclude that
% \emph{none} of them can lead to the state. In the future, we plan on exploring
% ways to help a user reason about unreachable states and ways to discover sets of
% unreachable states automatically.

### 2020-05-16 doc/sigmod_paper/sections/introduction.tex
First round of cuts.
The paper is now 8 pages without citations. We need 8 pages with
citations, so we need to trim another page or so. I'll probably shrink
the evaluation a bit more, shrink the related works a bit more, shrink
segmented invariant confluence a bit more and see what we end up with.

In this paper, we take a step back and study the underlying reason \emph{why}
\invariantclosure{} is not necessary for \invariantconfluence{}.
%
% We find that \invariantconfluence{} is fundamentally a reachability property,
% checking whether certain values of our replicated object can actually be
% obtained in the execution of a system. We discover that unreachable, yet
% invariant satisfying, states cause \invariantclosure{} to be an unnecessary
% condition.
%
Using this understanding, we construct a set of modest conditions under which
\invariantclosure{} and \invariantconfluence{} are in fact \emph{equivalent},
allowing us to reduce the problem of determining \invariantconfluence{} to that
of determining \invariantclosure{}.
%
Then, we use these conditions to design a general-purpose interactive
\invariantconfluence{} decision procedure and a new sufficient condition for
\invariantconfluence{}, dubbed \emph{\mergereducibility}. \Mergereducibility{}
covers some cases that are not covered by \invariantclosure{}, and it can be
checked automatically.

@@

Finally, we present Lucy: an implementation of our decision procedures and a
system for replicating \invariantconfluent{} and segmented
\invariantconfluent{} objects. Using Lucy, we find that our decision
procedures can efficiently handle a wide range of common workloads. For
example, in \secref{Evaluation}, we apply Lucy to foreign key constraints,
escrow transactions, an auction application, and the TPC-C benchmark. Lucy
processes these workloads in less than half a second, and no workload requires
more than 66 lines of code to specify. Moreover, we find that segmented
\invariantconfluent{} replication can achieve 10x to 100x more throughput than
linearizable replication for low-coordination workloads.

In closing, here is an outline of the paper and of our contributions:
%
We propose a novel expression-oriented definition of \invariantconfluence{}
that is both formal and simple (\secref{InvariantConfluence}).
%
We develop an understanding of why \invariantclosure{} is not necessary for
\invariantconfluence{} and use this understanding to develop conditions under
which it is both necessary and sufficient (\secref{InvariantClosure}).
%
We exploit these conditions to design a general-purpose interactive decision
procedure for \invariantconfluence{} (\secref{InteractiveDecisionProcedure}).
%
We again exploit these conditions to design a novel non-trivial sufficient
condition for \invariantconfluence{}, called \mergereducibility.
%
We present segmented \invariantconfluence{}: a generalization of
\invariantconfluence{} that uses a small amount of coordination to maintain
invariants for replicated objects that are otherwise not \invariantconfluent{}
(\secref{SegmentedInvariantConfluence}).
%
We evaluate our methods using a prototype implementation called Lucy
(\secref{Evaluation}).

>>>>

In this paper, we take a step back and study the underlying reason \emph{why}
\invariantclosure{} is not necessary for \invariantconfluence{}.
%
% We find that \invariantconfluence{} is fundamentally a reachability property,
% checking whether certain values of our replicated object can actually be
% obtained in the execution of a system. We discover that unreachable, yet
% invariant satisfying, states cause \invariantclosure{} to be an unnecessary
% condition.
%
Using this understanding, we construct a set of modest conditions under which
\invariantclosure{} and \invariantconfluence{} are in fact \emph{equivalent},
allowing us to reduce the problem of determining \invariantconfluence{} to that
of determining \invariantclosure{}.
%
Then, we use these conditions to design a general-purpose interactive
\invariantconfluence{} decision procedure.

@@

Finally, we present Lucy: an implementation of our decision procedures and a
system for replicating \invariantconfluent{} and segmented
\invariantconfluent{} objects. Using Lucy, we find that our decision procedures
can efficiently handle a wide range of common workloads.  For example, in
\secref{Evaluation}, we apply Lucy to foreign key constraints and escrow
transactions. Lucy processes these workloads in less than half a second, and
neither workload requires more than 66 lines of code to specify. Moreover, we
find that segmented \invariantconfluent{} replication can achieve 10x to 100x
more throughput than linearizable replication for low-coordination workloads.

% In closing, here is an outline of the paper and of our contributions:
% %
% We propose a novel expression-oriented definition of \invariantconfluence{}
% that is both formal and simple (\secref{InvariantConfluence}).
% %
% We develop an understanding of why \invariantclosure{} is not necessary for
% \invariantconfluence{} and use this understanding to develop conditions under
% which it is both necessary and sufficient (\secref{InvariantClosure}).
% %
% We exploit these conditions to design a general-purpose interactive decision
% procedure for \invariantconfluence{} (\secref{InteractiveDecisionProcedure}).
% %
% We again exploit these conditions to design a novel non-trivial sufficient
% condition for \invariantconfluence{}, called \mergereducibility.
% %
% We present segmented \invariantconfluence{}: a generalization of
% \invariantconfluence{} that uses a small amount of coordination to maintain
% invariants for replicated objects that are otherwise not \invariantconfluent{}
% (\secref{SegmentedInvariantConfluence}).
% %
% We evaluate our methods using a prototype implementation called Lucy
% (\secref{Evaluation}).

### 2020-05-16 doc/sigmod_paper/sections/invariant_confluence.tex
First round of cuts.
The paper is now 8 pages without citations. We need 8 pages with
citations, so we need to trim another page or so. I'll probably shrink
the evaluation a bit more, shrink the related works a bit more, shrink
segmented invariant confluence a bit more and see what we end up with.

Note that by modelling a transaction $t$ as a function $S \to S$, we focus
exclusively on the effects that a transaction has on the object (i.e.\
``writes'' to the object). Transactions are also free to read the value of the
object, but these reads are not captured by our model because, as we'll see,
they do not affect \invariantconfluence{}. For example, we could model any
read-only transaction as a function $t$ where $t(s) = s$ for every $s \in S$.

@@

Second, a server $p_i$ can send its state $s_i$ to another server $p_j$ with
state $s_j$ causing $p_j$ to transition from state $s_j$  to state $s_i \join
s_j$. Servers periodically merge states with one another in order to keep their
states loosely synchronized\footnote{%
  Notably, if $O$ is a CRDT---i.e. $O$ is a semilattice and every transaction
  $t \in T$ is inflationary---then this periodic merging ensures that $O$ is
  strongly eventually consistent~\cite{shapiro2011conflict}.
}.
Note that unlike with transactions, servers \emph{cannot} abort a merge; server
$p_j$ must transition from $s_j$ to $s_i \join s_j$ whether or not $s_i \join
s_j$ satisfies the invariant.

>>>>

% Note that by modelling a transaction $t$ as a function $S \to S$, we focus
% exclusively on the effects that a transaction has on the object (i.e.\
% ``writes'' to the object). Transactions are also free to read the value of the
% object, but these reads are not captured by our model because, as we'll see,
% they do not affect \invariantconfluence{}. For example, we could model any
% read-only transaction as a function $t$ where $t(s) = s$ for every $s \in S$.

@@

Second, a server $p_i$ can send its state $s_i$ to another server $p_j$ with
state $s_j$ causing $p_j$ to transition from state $s_j$  to state $s_i \join
s_j$. Servers periodically merge states with one another in order to keep their
states loosely synchronized.
% \footnote{%
%   Notably, if $O$ is a CRDT---i.e. $O$ is a semilattice and every transaction
%   $t \in T$ is inflationary---then this periodic merging ensures that $O$ is
%   strongly eventually consistent~\cite{shapiro2011conflict}.
% }.
Note that unlike with transactions, servers \emph{cannot} abort a merge; server
$p_j$ must transition from $s_j$ to $s_i \join s_j$ whether or not $s_i \join
s_j$ satisfies the invariant.

### 2020-05-16 doc/sigmod_paper/sections/segmented_invariant_confluence.tex
First round of cuts.
The paper is now 8 pages without citations. We need 8 pages with
citations, so we need to trim another page or so. I'll probably shrink
the evaluation a bit more, shrink the related works a bit more, shrink
segmented invariant confluence a bit more and see what we end up with.

The proof of the forward direction is exactly the same as the proof of
\thmref{IclosureImpliesIconfluence}. Transactions always maintain the
invariant, so if merge does as well, then every reachable state must satisfy
the invariant.
%
For the reverse direction, consider two arbitrary states $s_1, s_2 \in I$.
The two points are \TIcoreachable{}, so there exists some state $s_0$ from
which they can be reached. $O$ is \sTIconfluent{} and $s_1 \join s_2$ is
\sTIreachable{}, so it satisfies the invariant.

Using \thmref{ExtendedIclosureEquivalentIconfluence}, we develop
\algoref{ArbitraryStartInteractiveDecisionProcedure}: a natural generalization
of \algoref{InteractiveDecisionProcedure}.
\algoref{InteractiveDecisionProcedure} iteratively refines the set of
\emph{reachable} states whereas
\algoref{ArbitraryStartInteractiveDecisionProcedure} iteratively refines the
set of \emph{coreachable} states, but otherwise, the core of the two algorithms
is the same.\footnote{%
  Another small difference is that \IsIclosed{} behaves differently in
  \algoref{InteractiveDecisionProcedure} and
  \algoref{ArbitraryStartInteractiveDecisionProcedure}. In
  \algoref{ArbitraryStartInteractiveDecisionProcedure}, \IsIclosed{} returns a
  triple (closed, $s_1$, $s_2$). If closed is false, then $s_1, s_2 \in I$
  are two states not in $NR$ such that $I(s_1)$ and $I(s_2)$ but $\lnot I(s_1
  \join s_2)$. If no such states exist, then closed is true, and $s_1$ and
  $s_2$ are null.
}
Now, a segmented \invariantconfluence{} decision procedure, can simply invoke
\algoref{ArbitraryStartInteractiveDecisionProcedure} once on each segment.

@@

\subsection{Discussion and Limitations}
There are a few things worth noting about segmented \invariantconfluence{}, its
system model, and its decision procedure.
%
First, \invariantconfluence{} is a very coarse-grained property. If an object
is \invariantconfluent{}, then we can replicate it with no coordination. If it
is not \invariantconfluent{}, then we have no guarantees. There's no
in-between.  Segmented \invariantconfluence{}, on the other hand, is a much
more fine-grained property that can be applied to applications with varying
degrees of complexity. Segmented \invariantconfluence{} provides guarantees to
complex applications that require a large number of segments and to simple
applications with a smaller number of segments, whereas \invariantconfluence{}
only provides guarantees to applications that can be segmented into a single
segment.

Second, while our segmented \invariantconfluence{} decision procedure can help
decide whether or not an object is segmented \invariantconfluent{}, it cannot
currently help construct a segmentation. It is the responsibility of the
programmer to think of a segmentation that is amenable to segmented
\invariantconfluence{}. This can be an onerous process. In the future, we
plan to explore ways by which we can automatically suggest segmentations to the
application designer to ease this process.

\begin{techreport}

  Third, segmented \invariantconfluence{} naturally subsumes a distributed
  locking approach to replicating non-\invariantconfluent{} objects. This
  approach first recognizes which transactions cannot be safely executed
  concurrently and then requires them to acquire a distributed lock before
  executing~\cite{balegas2015putting, gotsman2016cause}. For example, in a
  banking application with the invariant that all balances remain non-negative,
  concurrent deposits are permitted, but concurrent withdrawals can lead to
  invariant violations. Thus, we require that withdrawals acquire a distributed
  lock before executing. This example is exactly the same as
  \exampleref{CounreachableExample} which we handled by simply removing
  withdrawal transactions from our segmentation's set of transactions.

  Fourth, we can integrate a couple of optimizations into our system model to
  further reduce the amount of coordination it requires. To begin, if a server
  with state $s_i$ and active segment $(I_i, T_i)$ receives a transaction $t
  \in I_i$ to execute, and $t(s_i)$ violates the active invariant but not the
  global invariant, instead of initiating a round of global coordination, $p_i$
  can simply buffer $t$ for re-execution at a later time. While this increases
  the latency required to execute $t$, it's possible that after other
  transactions are executed, re-executing $t$ may lead to a state that either
  satisfies the active invariant or violates the global invariant. In either
  case, a round of global coordination is avoided. Similarly, servers can
  buffer transactions that require global coordination, executing an entire
  batch of these transactions during a single round of global coordination.

  Fifth, a segmented \invariantconfluence{} decision procedure can also
  leverage \thmref{LatticeProperty} in addition to
  \algoref{ArbitraryStartInteractiveDecisionProcedure}. If an object $O$ meets
  criteria (1) - (3), then it is \sticonfluent{s}{T}{I} for every state $s \in
  I$.
\end{techreport}

>>>>

% The proof of the forward direction is exactly the same as the proof of
% \thmref{IclosureImpliesIconfluence}. Transactions always maintain the
% invariant, so if merge does as well, then every reachable state must satisfy
% the invariant.
% %
% For the reverse direction, consider two arbitrary states $s_1, s_2 \in I$.
% The two points are \TIcoreachable{}, so there exists some state $s_0$ from
% which they can be reached. $O$ is \sTIconfluent{} and $s_1 \join s_2$ is
% \sTIreachable{}, so it satisfies the invariant.

Using \thmref{ExtendedIclosureEquivalentIconfluence}, we develop
\algoref{ArbitraryStartInteractiveDecisionProcedure}: a natural generalization
of \algoref{InteractiveDecisionProcedure}.
\algoref{InteractiveDecisionProcedure} iteratively refines the set of
\emph{reachable} states whereas
\algoref{ArbitraryStartInteractiveDecisionProcedure} iteratively refines the
set of \emph{coreachable} states, but otherwise, the core of the two algorithms
is the same.
% \footnote{%
%   Another small difference is that \IsIclosed{} behaves differently in
%   \algoref{InteractiveDecisionProcedure} and
%   \algoref{ArbitraryStartInteractiveDecisionProcedure}. In
%   \algoref{ArbitraryStartInteractiveDecisionProcedure}, \IsIclosed{} returns a
%   triple (closed, $s_1$, $s_2$). If closed is false, then $s_1, s_2 \in I$
%   are two states not in $NR$ such that $I(s_1)$ and $I(s_2)$ but $\lnot I(s_1
%   \join s_2)$. If no such states exist, then closed is true, and $s_1$ and
%   $s_2$ are null.
% }
Now, a segmented \invariantconfluence{} decision procedure, can simply invoke
\algoref{ArbitraryStartInteractiveDecisionProcedure} once on each segment.

@@

% \subsection{Discussion and Limitations}
% There are a few things worth noting about segmented \invariantconfluence{}, its
% system model, and its decision procedure.
% %
% First, \invariantconfluence{} is a very coarse-grained property. If an object
% is \invariantconfluent{}, then we can replicate it with no coordination. If it
% is not \invariantconfluent{}, then we have no guarantees. There's no
% in-between.  Segmented \invariantconfluence{}, on the other hand, is a much
% more fine-grained property that can be applied to applications with varying
% degrees of complexity. Segmented \invariantconfluence{} provides guarantees to
% complex applications that require a large number of segments and to simple
% applications with a smaller number of segments, whereas \invariantconfluence{}
% only provides guarantees to applications that can be segmented into a single
% segment.
%
% Second, while our segmented \invariantconfluence{} decision procedure can help
% decide whether or not an object is segmented \invariantconfluent{}, it cannot
% currently help construct a segmentation. It is the responsibility of the
% programmer to think of a segmentation that is amenable to segmented
% \invariantconfluence{}. This can be an onerous process. In the future, we
% plan to explore ways by which we can automatically suggest segmentations to the
% application designer to ease this process.
